---
title: "Tufte Handout"
subtitle: "An implementation in R Markdown"
author: "Ankita Pal"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
  
bibliography: example.bib
link-citations: yes
---


```yaml
---
title: "An Example Using the Tufte Style"
author: "John Smith"
output:
  tufte::tufte_handout: default
  tufte::tufte_html: default
---
```
```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'),echo = FALSE,
                      comment = "%%",
                      warning = FALSE,
                      message = FALSE)
options(htmltools.dir.version = FALSE)
```
## Q1:Uses starwars dataset & tidyverse
## Q2:Has a plot and table
## Q4:Has a user-friendly, polished structure
## Q5:Has a step-up chunk, with 3+ settings
## Q6:Uses a template from the rticles/papaja/tufte pkg or similar



```{r, starwars-plot, fig.cap ='A ggplot ofStarwars data', message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
starwars %>% 
  filter(species == "Human") %>% 
ggplot() +
  aes(x = height, 
      y = mass) +
  geom_point()
```


## Q2:Has a plot and table


```{r starwars-tbl}
starwars %>% 
  filter(species == "Human")  %>% 
  select(name, 
         height, 
         mass, 
         homeworld) %>% 
  knitr::kable(caption = "A knitr kable table of starwars data")
```




## Q3:Has two in-text citations using bibtex
2 reference [@echeverria2017discovery; @barba2018terminologies].

plesser says blah [-@plesser2018reproducibility].


References cited

## Q6:Uses code from an external R script file and knitr::read_chunk()

```{r load-data, message=FALSE}
library(tidyverse)
data <- data(starwars)
knitr::read_chunk("ext_file.R")
```

### A ggplot of starwars stuff
## Q7:Uses knitr caching

```{r starwars-plot, dependson="load-data", fig.align='center', cache=TRUE}
```
