---
title: "Tufte Handout"
subtitle: "An implementation in R Markdown"
output:
  bookdown::html_document2:
    fig_caption: yes
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: example.bib
link-citations: yes
author: "Ankita Pal"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'),echo = FALSE,
                      comment = "%%",
                      warning = FALSE,
                      message = FALSE)
options(htmltools.dir.version = FALSE)
```
## Q1:Uses starwars dataset & tidyverse
## Q2:Has a plot and table with captions and cross-references
## Q4:Has a user-friendly, polished structure
## Q5:Has a step-up chunk, with 3+ settings
## Q6:Uses a template from the rticles/papaja/tufte pkg or similar
## Q7:Uses knitr caching


```{r, starwars-plot, fig.cap ='A ggplot ofStarwars data', message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
starwars %>% 
  filter(species == "Human") %>% 
ggplot() +
  aes(x = height, 
      y = mass) +
  geom_point()
```

We can see in Figure \@ref(fig:starwars-plot)...

We need a chunk label and a chunk caption for cross-referencing to work!

```{r starwars-tbl}
starwars %>% 
  filter(species == "Human")  %>% 
  select(name, 
         height, 
         mass, 
         homeworld) %>% 
  knitr::kable(caption = "A knitr kable table of starwars data")
```

We can see in Table \@ref(tab:starwars-tbl) …


## Q3:Has two in-text citations using bibtex

2 reference [@echeverria2017discovery; @barba2018terminologies].

plesser says blah [-@plesser2018reproducibility].


References cited

## Q6:Uses code from an external R script file and knitr::read_chunk()

```{r load-data, message=FALSE}
library(tidyverse)
data <- data(starwars)
knitr::read_chunk("ext_file.R")
```

# A ggplot of starwars stuff

```{r starwars-plot, dependson="load-data", fig.align='center', cache=TRUE}
```